### 2024-11-15 conteudo/eval/eval.tex
remove TODO's
reforce that we do not expect good results in T3/T4 types

\todo[inline]{Juntei os capítulos; veja se consegue colocar algo aqui no início; não sei se final remarks é o melhor nome para a segunda secao aqui}

@@

In this section, we present the test results of our tool performance, following the methodology described in Chapter \ref{cha:method}. First, we provide the results obtained by our tool on the BigCloneBench dataset \citep{bigclonebench}, which serves as a standard reference in the literature \citep{litreview}. Second, we discuss the results from our empirical analysis. Finally, we triangulate the data, analyzing our findings regarding the tool performance.

\subsection{Tool Results on the BigCloneBench Dataset}

>>>>

@@

In this section, we present the test results of our tool performance, following the 
methodology described in Chapter \ref{cha:method}. First, we provide the results 
obtained by our tool on the BigCloneBench dataset \citep{bigclonebench}, which 
serves as a standard reference in the literature \citep{litreview}. Second, we 
discuss the results from our empirical analysis. Finally, we triangulate the data, 
analyzing our findings regarding the tool performance. 
As a reminder, we only expect our tool to yield good results for Type-1 and Type-2,
as mentioned in \ref{subsec:code_finder}.
